---
title: "5_ScenarioAnalysis"
author: "Billy Geary"
date: "20/11/2021" 
output: html_document
---

```{r, setup}
library(brms)
library(piecewiseSEM)
library(tidybayes)
library(tidyverse)
```

# Read in SEM for Prediction
```{r}
data = read.csv("~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/UpperWarrenSEM/Data_Clean/transect.sem.data.Dec2022.csv")
load("~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/UpperWarrenSEM/Data_Clean/best.sem.fit.Dec2022.Rdata")
```
# Baseline Scenario
```{r}
newdata = data.frame(BaitIntensity.Transect.Twelve = mean(data$BaitIntensity.Transect.Twelve),
                     mean.smNDVI = mean(data$mean.smNDVI),
                     prop.pasture.1km = mean(data$prop.pasture.1km),
                     DistCentroidPasture = mean(data$DistCentroidPasture),
                     valleys.prop.area = mean(data$valleys.prop.area),
                     prop_moderate_transect = mean(data$prop_moderate_transect),
                     tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                     prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                     prop_severe_transect = mean(data$prop_severe_transect),
                     prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                     Effort = 200,
                     ndvi.monthly.anomaly = mean(data$ndvi.monthly.anomaly),
                     Woylie_Abundance = mean(data$Woylie_Abundance),
                     Chuditch_Abundance = mean(data$Chuditch_Abundance),
                     Phase = NA)


fauna_base <-fitted(best_sem, newdata=newdata,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)

#to minimize excess uncertainty
fauna_base_out <- data.frame(Woylie = fauna_base[, ,1],
                         Chuditch = fauna_base[, ,2],
                         Koomal = fauna_base[, ,3],
                         Quenda = fauna_base[, ,4],
                         Scenario = "Base")
```


# Scenario 1: Reduction in Rainfall Anomaly
50% below average
```{r}
# Step 1 - Rainfaill Anomaly -> NDVI anomaly
newdata = data.frame(rain.anomaly.twelve =-0.2, ndvi.monthly.anomaly=NA, Phase = NA)
ndvi_pred <- fitted(best_sem, newdata=newdata,
             resp = "scalendvimonthlyanomaly", ndraws = 1000, 
             summary = FALSE, re_formula = NA)

# Step 2 - NDVI anomaly -> Animal abundance
newdata2 <- expand.grid(rain.anomaly.twelve = newdata$rain.anomaly.twelve, 
                        ndvi.monthly.anomaly = as.vector(ndvi_pred))

newdata2 = newdata2 %>% mutate(BaitIntensity.Transect.Twelve = mean(data$BaitIntensity.Transect.Twelve),
                               mean.smNDVI = mean(data$mean.smNDVI),
                               prop.pasture.1km = mean(data$prop.pasture.1km),
                               DistCentroidPasture = mean(data$DistCentroidPasture),
                               valleys.prop.area = mean(data$valleys.prop.area),
                               prop_moderate_transect = mean(data$prop_moderate_transect),
                               tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                               prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                               prop_severe_transect = mean(data$prop_severe_transect),
                               prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                               Effort = 200,
                               Chuditch_Abundance = mean(data$Chuditch_Abundance),
                               Woylie_Abundance = mean(data$Woylie_Abundance),
                               Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)

#to minimize excess uncertainty
fauna_rain_out <- data.frame(Woylie = as.matrix(diag(fauna_pred[, ,1])),
                         Chuditch = as.matrix(diag(fauna_pred[, ,2])),
                         Koomal = as.matrix(diag(fauna_pred[, ,3])),
                         Quenda = as.matrix(diag(fauna_pred[, ,4])),
                         Scenario = "Low Rainfall")

combined_scenarios = rbind(fauna_base_out, fauna_rain_out)

```

# Scenario 2: Increase in Moderate Fire
```{r}
newdata2 = data.frame(prop_moderate_transect = 0.5,
                      prop_severe_transect = mean(data$prop_severe_transect),
                      prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = mean(data$BaitIntensity.Transect.Twelve),
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      ndvi.monthly.anomaly = mean(data$ndvi.monthly.anomaly),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
fauna_modfire_out <- data.frame(Woylie = as.matrix(fauna_pred[, ,1]),
                         Chuditch = as.matrix(fauna_pred[, ,2]),
                         Koomal = as.matrix(fauna_pred[, ,3]),
                         Quenda = as.matrix(fauna_pred[, ,4]),
                         Scenario = "Increased Moderate Fire")

```

# Scenario 3: Increase in Severe Fire
```{r}
newdata2 = data.frame(prop_moderate_transect = mean(data$prop_moderate_transect),
                      prop_severe_transect = 0.5,
                      prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = mean(data$BaitIntensity.Transect.Twelve),
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      ndvi.monthly.anomaly = mean(data$ndvi.monthly.anomaly),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
fauna_sevfire_out <- data.frame(Woylie = as.matrix(fauna_pred[, ,1]),
                         Chuditch = as.matrix(fauna_pred[, ,2]),
                         Koomal = as.matrix(fauna_pred[, ,3]),
                         Quenda = as.matrix(fauna_pred[, ,4]),
                         Scenario = "Increased Severe Fire")

```

# Scenario 4: Increase in Repeat Fire
```{r}
newdata2 = data.frame(prop_moderate_transect = mean(data$prop_moderate_transect),
                      prop_severe_transect = mean(data$prop_severe_transect),
                      prop.burnttwice.500m.transect = 0.5,
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = mean(data$BaitIntensity.Transect.Twelve),
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      ndvi.monthly.anomaly = mean(data$ndvi.monthly.anomaly),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
fauna_freqfire_out <- data.frame(Woylie = as.matrix(fauna_pred[, ,1]),
                         Chuditch = as.matrix(fauna_pred[, ,2]),
                         Koomal = as.matrix(fauna_pred[, ,3]),
                         Quenda = as.matrix(fauna_pred[, ,4]),
                         Scenario = "Increased Short-interval Fire")

```

# Scenario 5: Increased Baiting Intensity
```{r}
newdata2 = data.frame(prop_moderate_transect = mean(data$prop_moderate_transect),
                      prop_severe_transect = mean(data$prop_severe_transect),
                      prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = 45,
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      ndvi.monthly.anomaly = mean(data$ndvi.monthly.anomaly),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
fauna_baiting_out <- data.frame(Woylie = as.matrix(fauna_pred[, ,1]),
                         Chuditch = as.matrix(fauna_pred[, ,2]),
                         Koomal = as.matrix(fauna_pred[, ,3]),
                         Quenda = as.matrix(fauna_pred[, ,4]),
                         Scenario = "Increased Baiting Intensity")

```

# Scenario 6: Increase in Severe Fire and Baiting Intensity
```{r}
newdata2 = data.frame(prop_moderate_transect = mean(data$prop_moderate_transect),
                      prop_severe_transect = 0.5,
                      prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = 45,
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      ndvi.monthly.anomaly = mean(data$ndvi.monthly.anomaly),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
fauna_sevfirebaiting_out <- data.frame(Woylie = as.matrix(fauna_pred[, ,1]),
                         Chuditch = as.matrix(fauna_pred[, ,2]),
                         Koomal = as.matrix(fauna_pred[, ,3]),
                         Quenda = as.matrix(fauna_pred[, ,4]),
                         Scenario = "Increased Severe Fire + Baiting Intensity")

```

# Scenario 7: Low Rainfall + Severe Fire
```{r}

# Step 1 - Rainfaill Anomaly -> NDVI anomaly
newdata = data.frame(rain.anomaly.twelve =-0.2, ndvi.monthly.anomaly=NA, Phase = NA)
ndvi_pred <- fitted(best_sem, newdata=newdata,
             resp = "scalendvimonthlyanomaly", ndraws = 1000, 
             summary = FALSE, re_formula = NA)

# Step 2 - NDVI anomaly -> Animal abundance
newdata2 <- expand.grid(rain.anomaly.twelve = newdata$rain.anomaly.twelve, 
                        ndvi.monthly.anomaly = as.vector(ndvi_pred))

newdata2 = newdata2 %>% mutate(prop_moderate_transect = mean(data$prop_moderate_transect),
                      prop_severe_transect = 0.5,
                      prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = mean(data$BaitIntensity.Transect.Twelve),
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
#to minimize excess uncertainty
fauna_droughtsevfire_out <- data.frame(Woylie = as.matrix(diag(fauna_pred[, ,1])),
                         Chuditch = as.matrix(diag(fauna_pred[, ,2])),
                         Koomal = as.matrix(diag(fauna_pred[, ,3])),
                         Quenda = as.matrix(diag(fauna_pred[, ,4])),
                         Scenario = "Low Rainfall + Increased Severe Fire")

```

# Scenario 8: Moderate Fire Current Policy
```{r}
newdata2 = data.frame(prop_moderate_transect = 0.25,
                      prop_severe_transect = mean(data$prop_severe_transect),
                      prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = mean(data$BaitIntensity.Transect.Twelve),
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      ndvi.monthly.anomaly = mean(data$ndvi.monthly.anomaly),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
fauna_modfirepolicy_out <- data.frame(Woylie = as.matrix(fauna_pred[, ,1]),
                         Chuditch = as.matrix(fauna_pred[, ,2]),
                         Koomal = as.matrix(fauna_pred[, ,3]),
                         Quenda = as.matrix(fauna_pred[, ,4]),
                         Scenario = "Moderate Fire")

```

# Scenario 9: Low Rainfall + Current Fire Policy
```{r}

# Step 1 - Rainfaill Anomaly -> NDVI anomaly
newdata = data.frame(rain.anomaly.twelve =-0.2, ndvi.monthly.anomaly=NA, Phase = NA)
ndvi_pred <- fitted(best_sem, newdata=newdata,
             resp = "scalendvimonthlyanomaly", ndraws = 1000, 
             summary = FALSE, re_formula = NA)

# Step 2 - NDVI anomaly -> Animal abundance
newdata2 <- expand.grid(rain.anomaly.twelve = newdata$rain.anomaly.twelve, 
                        ndvi.monthly.anomaly = as.vector(ndvi_pred))

newdata2 = newdata2 %>% mutate(prop_moderate_transect = 0.25,
                      prop_severe_transect = mean(data$prop_severe_transect),
                      prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = mean(data$BaitIntensity.Transect.Twelve),
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
#to minimize excess uncertainty
fauna_droughtmodfirepolicy_out <- data.frame(Woylie = as.matrix(diag(fauna_pred[, ,1])),
                         Chuditch = as.matrix(diag(fauna_pred[, ,2])),
                         Koomal = as.matrix(diag(fauna_pred[, ,3])),
                         Quenda = as.matrix(diag(fauna_pred[, ,4])),
                         Scenario = "Low Rainfall + Moderate Fire")

```

# Scenario 10: Low Rainfall + Severe Fire + Baiting Intensity
```{r}

# Step 1 - Rainfaill Anomaly -> NDVI anomaly
newdata = data.frame(rain.anomaly.twelve =-0.2, ndvi.monthly.anomaly=NA, Phase = NA)
ndvi_pred <- fitted(best_sem, newdata=newdata,
             resp = "scalendvimonthlyanomaly", ndraws = 1000, 
             summary = FALSE, re_formula = NA)

# Step 2 - NDVI anomaly -> Animal abundance
newdata2 <- expand.grid(rain.anomaly.twelve = newdata$rain.anomaly.twelve, 
                        ndvi.monthly.anomaly = as.vector(ndvi_pred))

newdata2 = newdata2 %>% mutate(prop_moderate_transect = mean(data$prop_moderate_transect),
                      prop_severe_transect = 0.5,
                      prop.burnttwice.500m.transect = mean(data$prop.burnttwice.500m.transect),
                      tsf.cat.shannon.diversity = mean(data$tsf.cat.shannon.diversity),
                      BaitIntensity.Transect.Twelve = 45,
                      mean.smNDVI = mean(data$mean.smNDVI),
                      prop.pasture.1km = mean(data$prop.pasture.1km),
                      DistCentroidPasture = mean(data$DistCentroidPasture),
                      valleys.prop.area = mean(data$valleys.prop.area),
                      prop.20yrsharvest.500m.transect = mean(data$prop.20yrsharvest.500m.transect),
                      Effort = 200,
                      Woylie_Abundance = mean(data$Woylie_Abundance),
                      Chuditch_Abundance = mean(data$Chuditch_Abundance),
                      Phase = NA)

fauna_pred <- fitted(best_sem, newdata=newdata2,
             resp = c("WoylieAbundance","ChuditchAbundance", "KoomalAbundance", "QuendaCaps"), ndraws = 1000, 
             summary = FALSE, re_formula = NA)


#to minimize excess uncertainty
#to minimize excess uncertainty
fauna_droughtsevfirebaiting_out <- data.frame(Woylie = as.matrix(diag(fauna_pred[, ,1])),
                         Chuditch = as.matrix(diag(fauna_pred[, ,2])),
                         Koomal = as.matrix(diag(fauna_pred[, ,3])),
                         Quenda = as.matrix(diag(fauna_pred[, ,4])),
                         Scenario = "Low Rainfall + Increased Severe Fire + Baiting")

```

# Plots

```{r}
combined_scenarios = rbind(fauna_base_out, 
                           fauna_rain_out, 
                           fauna_modfire_out, 
                           fauna_sevfire_out, 
                           fauna_freqfire_out,
                           fauna_baiting_out,
                           fauna_sevfirebaiting_out,
                           fauna_droughtsevfire_out,
                           fauna_droughtsevfirebaiting_out,
                           fauna_modfirepolicy_out, 
                           fauna_droughtmodfirepolicy_out)

scenario_plot = function(input.data, species,ylab, ymax){
  plot.data = input.data
  spp = species
  pal = viridisLite::viridis(11)
  plot.data = plot.data %>% as.data.frame() %>% pivot_longer(cols=1:4, names_to="Species") %>% 
    mutate(Scenario = forcats::fct_relevel(Scenario, 
                                  "Low Rainfall + Increased Severe Fire + Baiting",
                                  "Low Rainfall + Increased Severe Fire",
                                  "Increased Severe Fire + Baiting Intensity",
                                  "Increased Short-interval Fire", 
                                  "Increased Severe Fire", 
                                  "Increased Moderate Fire", 
                                  "Low Rainfall + Moderate Fire",
                                  "Increased Baiting Intensity", 
                                  "Moderate Fire",
                                  "Low Rainfall", 
                                  "Base")) %>%
    filter(Species == spp)
  median.base = median(filter(plot.data, Scenario=="Base")$value)
  plot = plot.data %>%
    ggplot(aes(y=value, x=Scenario, fill=Scenario)) + 
    geom_hline(yintercept = median.base, linetype = 'dashed') + 
    geom_boxplot(width = .25, outlier.shape = NA, alpha = 0.7) +
    ggdist::stat_halfeye(adjust = .5, width = .75,.width = 0,justification = -.2,point_colour = NA, alpha=0.7) + 
    scale_colour_manual(values = pal) + scale_fill_manual(values = pal) +
    ylab(ylab) + xlab("Scenario") + ylim(c(0,ymax)) +
    cowplot::theme_cowplot() + theme(legend.position = "none") + coord_flip()
  plot
}

a = scenario_plot(combined_scenarios, "Woylie", "Predicted Abundance", 100)
b = scenario_plot(combined_scenarios, "Chuditch", "Predicted Abundance", 40)
c = scenario_plot(combined_scenarios, "Koomal", "Predicted Abundance", 250)
d = scenario_plot(combined_scenarios, "Quenda", "Predicted Activity", 2)

plot.out = cowplot::plot_grid(a,b,c,d,labels=c("a) Woylie", "b) Chuditch", "c) Koomal", "d) Quenda"), align='h')

ggsave("Fig4_ScenarioAnalysis_New.pdf", plot=plot.out,
       path="~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/UpperWarrenSEM/Outputs", 
       scale=2,width=7, height=4.5, units='in',dpi=300)

```

# Scenario information plots
```{r}
rainfall.plot = ggplot(data) + geom_histogram(aes(x=rain.anomaly.twelve)) + 
  geom_vline(xintercept=-0.2, linetype='dashed') + theme_classic() + xlab("12 month Rainfall Anomaly")
modsev.plot = ggplot(data) + geom_histogram(aes(x=prop_moderate_transect)) + 
  geom_vline(xintercept=0.25, linetype='dashed') + geom_vline(xintercept=0.5, linetype='dashed') + 
  theme_classic() + xlab('Proportion Burnt Moderately')
highsev.plot = ggplot(data) + geom_histogram(aes(x=prop_severe_transect)) + 
  geom_vline(xintercept =0.5, linetype='dashed') + 
  theme_classic() + xlab('Proportion Burnt Severely')
bait.plot = ggplot(data) + geom_histogram(aes(x=BaitIntensity.Transect.Twelve)) + 
  geom_vline(xintercept =45, linetype='dashed') + 
  theme_classic() + xlab('Baiting Intensity')

hist.plot = cowplot::plot_grid(rainfall.plot, modsev.plot, highsev.plot,bait.plot, nrow=2)
hist.plot
```
